3D Magnetic modelling of ellipsoidal bodies

### 2017-01-27 manuscript/manuscript.tex
elements of the N ddagger depolarizatin tensor
preliminary version of introduction

@@

The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
depend on the orientation angles 
$\alpha$, $\beta$, $\gamma$ and are defined 
as follows \citep{clark1986}:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v1_triaxial_prolate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v2_triaxial_prolate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_triaxial_prolate}
\end{equation}
For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
$\mathbf{V}$ (Eq. \ref{eq:A}) is calculated by using Eqs.
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate} as follows:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{1} & \mathbf{v}_{2} & \mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_triaxial_prolate}
\end{equation}
Similarly, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
prolate ellipsoids (i.e., $a > b = c$) is calculated according
to Equation \ref{eq:V_triaxial_prolate} by using Equations
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ 
\citep{emerson1985}.
Finally, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
oblate ellipsoids (i.e., $a < b = c$) is calculated by 
using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
\citep{emerson1985}:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{2} & \mathbf{v}_{1} & -\mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_oblate}
\end{equation}
The orientation of the semi-axes $a$, $b$, and $c$ are defined 
by the first, second, and third columns of the matrix 
$\mathbf{V}$ given by Equation \ref{eq:V_triaxial_prolate},
in the case of a triaxial or prolate ellipsoid, or the
matrix $\mathbf{V}$ given by Equation \ref{eq:V_oblate},
in the case of an oblate ellipsoid.

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Equation \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.
%Similarly, we may properly use the orthogonality of 
%matrix $\mathbf{V}$ to transform a generic 
%linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$,
%referred to the main coordinate system, into a new
%linear system 
%$\tilde{\mathbf{M}} \, \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$,
%referred to a local coordinate system, 
%as follows:
%\begin{equation}
%\underbrace{\mathbf{V}^{\top} \mathbf{M} \mathbf{V}}_{\tilde{\mathbf{M}}} \, 
%\underbrace{\mathbf{V}^{\top} \mathbf{p}}_{\tilde{\mathbf{p}}} = 
%\underbrace{\mathbf{V}^{\top} \mathbf{d}}_{\tilde{\mathbf{d}}} \: .
%\label{eq:matrix-transformation}
%\end{equation}

@@

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any body uniformly magnetized in a given direction.
By presuming that this uniform magnetization is due to
induction, he postulated that the resulting magnetic
field (intensity) at all points within the body must
also be uniform and parallel the magnetization, which
results that the gravitational potential $U$ at points
within the body must be a quadratic function of the
spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
affirm that the only finite bodies having a gravitational
potential with this property and that, as a consequence,
can be uniformly magnetized in the presence of a uniform and 
static magnetic field are the ones bounded by surfaces 
of second degree, which are ellipsoids.

Consider a magnetized ellipsoid immersed in
a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
This uniform field can be, for example, the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:phi-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
the coordinates of a point located within the volume $\vartheta$
of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Equation \ref{eq:phi-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896}.

@@

The scalar function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\dagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{0}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in V \: ,
\label{eq:fi-tilde}
\end{equation}
where
\begin{equation}
R(u) = \sqrt{\left( a^{2} + u \right)\left( b^{2} + u \right)\left( c^{2} + u \right)} \: .
\label{eq:R}
\end{equation}
This function represents the gravitational potential
that would be produced by the ellipsoidal body at
points located within its volume $\vartheta$ if it
had a uniform density equal to the inverse of the
gravitational constant.
Notice that, in this case, the gravitational potential
is a quadratic function of the spatial coordinates
$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
postulate about uniformly magnetized ellipsoids.
In a similar way, the function $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\ddagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{\lambda}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in V \: ,
\label{eq:fe-tilde}
\end{equation}
where $R(u)$ is defined by Equation \ref{eq:R} and the
parameter $\lambda$ is defined according to the
ellipsoid type as a function of the spatial coordinates
 $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ (see Appendix B). 
For readers interested in additional information about the 
parameter $\lambda$, we recommend \citet[p.~234]{webster1904},
\citet[p.~184]{kellogg1929} and \citet{clark1986}.

The second important coordinate transformation is defined
with respect to Equation \ref{eq:H-M-uniform}.
By properly using the orthogonality of matrix $\mathbf{V}$ 
(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) can be transformed
from the main coordinate system to a local coordinate system
as follows:
\begin{equation}
\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
_{\tilde{\mathbf{K}}} \; 
\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
_{\tilde{\mathbf{H}}^{\dagger}} \: ,
\label{eq:H-tilde}
\end{equation}
where the superscript "$\sim$" denotes quantities
referred to the respective local coordinate system.

In Equation \ref{eq:H-tilde}, the transformed
depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
is calculated as a function of the original depolarization
tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
are calculated as a function of the second derivatives of the
function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
which is defined in the main coordinate system.
It can be shown (Appendix A), however, that the
elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
as follows:
\begin{equation}
\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
\label{eq:nij-tilde}
\end{equation}
where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Equation \ref{eq:fi-tilde}
or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
point located within or without the volume $\vartheta$ of the
ellipsoidal body.

@@

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Equation \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ represents the
transformed depolarization tensor evaluated within 
the volume $\vartheta$ of the ellipsoidal body. The elements
of $\tilde{\mathbf{N}}^{\dagger}$ will be presented in a 
latter section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Equation 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.

>>>>

Based on the mathematical theory of the magnetic 
induction developed by \citet{poisson1824}, 
\citet{maxwell1873} affirmed that, if $U$ is the 
gravitational potential produced by any body 
with uniform density $\rho$ and arbitrary shape at 
a point $(x, y, z)$, then $-\frac{\partial U}{\partial x}$
is the magnetic scalar potential produced 
at the same point by the same body 
if it has a uniform magnetization oriented along $x$ 
with intensity $\rho$.
\citet{maxwell1873} generalized this idea as a way
of determining the magnetic scalar potential produced
by any body uniformly magnetized in a given direction.
By presuming that this uniform magnetization is due to
induction, he postulated that the resulting magnetic
field (intensity) at all points within the body must
also be uniform and parallel to the magnetization.
As a consequence, the gravitational potential 
$U$ at points within the body must be a quadratic 
function of the spatial coordinates.
Apparently, \citet{maxwell1873} was the first one to
postulate that ellipsoids are the only finite bodies 
having a gravitational potential which satisfies this 
property and hence can be uniformly magnetized 
in the presence of a uniform magnetic field.

This property can be extended to other bodies
whose shape derives from an ellipsoid 
(e.g., spheres, elliptic cylinders), however all the
remaining non-ellipsoidal bodies cannot be
uniformly magnetized in the presence of a uniform
inducing field \citep{jahren1963, schlomann1965, clark1999}.

Self-demagnetization demagnetization gives rise to shape 
anisotropy.

Self-demagnetization is a function of the shape of 
the body.

The self-demagnetization contributes to decrease the
magnitude of the magnetization along the shortest 
dimensions of a body.

Ellipsoids are the only bodies which enable an
analytical computation of its self-demagnetization.

Ellipsoids can assume a wide range of shapes and
therefore can be used to represent different geological
bodies.

It is well-known by that the self-demagnetization can 
be neglected if the body has a susceptibility lower 
than 0.1 SI \citep{austin2014, clark2014, clark1986, 
emerson1985, eskola1980, guo1998, guo2001, purss2005,
hillan2013}.

However, neglecting the self-demagnetization in
geological bodies with high susceptibilities (> 0.1 SI) 
may strongly mislead the results obtained from
magnetic methods.

\citet{farrar1979} demonstrated the importance of the
ellipsoidal model in taking into account the 
self-demagnetization and determining reliable 
drilling directions on the Tennant Creek field, 
Australia.

Posteriorly, \citet{hoschke1991} also showed how the
ellipsoidal model proved to be highly successful in
locating and defining ironstone bodies in the
Tennant Creek field.

\citet{clark2000} provides a good discussion about the
influence of the self-demagnetization in magnetic
interpretation of the Osborne copper-gold deposit, 
Australia. This deposit is hosted by ironstone 
bodies that have very high susceptibility.
According to \citet{clark2000}, neglecting the effects 
of self-demagnetisation led errors of $\approx 55^{\circ}$
in the interpreted dip.

Based on magnetic modelling and rock property 
measurements, \citet{austin2014} showed that,
contrary to previous interpretations, the magnetization
of the Candelaria iron oxide copper-gold deposit, 
Chile, is not dominated by the induced component.
Rather, the deposit has a relatively weak remanent 
magnetization and is strongly affected by 
self-demagnetization.

These examples show the practical importance of
self-demagnetization for the correct interpretation
of magnetic data produced by geological bodies having
high susceptibilities.

These examples also show the importance of the ellipsoidal
model in producing trustworthy geological models of orebodies,
which may save significant cost associated with drilling.

%The ellipsoidal model ability in analytically
%incorporating the self-demagnetization...
%FALAR DA APLICACAO DIDATICA

%Apesar da grande aplicabilidade do modelo elipsoidal 
%na geofísica, apenas alguns softwares proprietários 
%possuem sua implementação. Neste sentido, este trabalho 
%tem a finalidade de disponibilizar uma ferramenta de 
%código aberto, que poderá ser utilizada livremente 
%por toda a comunidade geofísica. 
%VER COMO AQUELE CARA DA ISOSTASIA ESCREVEU

@@

The vectors $\mathbf{v}_{1}$, $\mathbf{v}_{2}$, and $\mathbf{v}_{3}$ 
depend on the orientation angles 
$\alpha$, $\beta$, $\gamma$ and are defined 
as follows \citep{clark1986}:
\begin{equation}
\mathbf{v}_{1} = \left[\begin{array}{c} 
                  -\cos\alpha \; \cos\delta \\
                  -\sin\alpha \; \cos\delta \\
                  -\sin\delta
                  \end{array} \right] \: ,
\label{eq:v1_triaxial_prolate}
\end{equation}
\begin{equation}
\mathbf{v}_{2} = \left[\begin{array}{c} 
                  \cos\alpha \; \cos\gamma \; \sin\delta + \sin\alpha \; \sin\gamma \\                   
                  \sin\alpha \; \cos\gamma \; \sin\delta - \cos\alpha \; \sin\gamma \\ 
                  -\cos\gamma \; \cos\delta
                  \end{array} \right] \: ,
\label{eq:v2_triaxial_prolate}
\end{equation}                   
\begin{equation}                    
\mathbf{v}_{3} = \left[\begin{array}{c} 
                  \sin\alpha \; \cos\gamma - \cos\alpha \; \sin\gamma \; \sin\delta \\                    
                  -\cos\alpha \; \cos\gamma - \sin\alpha \; \sin\gamma \; \sin\delta \\
                  \sin\gamma \; \cos\delta
                  \end{array} \right] \: .
\label{eq:v3_triaxial_prolate}
\end{equation}
For triaxial ellipsoids (i.e., $a > b > c$), the orthogonal matrix
$\mathbf{V}$ (Eq. \ref{eq:A}) is calculated by using Eqs.
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate} as follows:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{1} & \mathbf{v}_{2} & \mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_triaxial_prolate}
\end{equation}
Similarly, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
prolate ellipsoids (i.e., $a > b = c$) is calculated according
to Eq. \ref{eq:V_triaxial_prolate} by using Eqs.
\ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, but with $\gamma = 0^{\circ}$ 
\citep{emerson1985}.
Finally, the matrix $\mathbf{V}$ (Eq. \ref{eq:A}) for
oblate ellipsoids (i.e., $a < b = c$) is calculated by 
using Eqs. \ref{eq:v1_triaxial_prolate}, \ref{eq:v2_triaxial_prolate}, and
\ref{eq:v3_triaxial_prolate}, with $\gamma = 0^{\circ}$, as follows
\citep{emerson1985}:
\begin{equation}
\mathbf{V} = \left[ \begin{array}{ccc}
\mathbf{v}_{2} & \mathbf{v}_{1} & -\mathbf{v}_{3}
\end{array} \right] \: .
\label{eq:V_oblate}
\end{equation}
The orientation of the semi-axes $a$, $b$, and $c$ are defined 
by the first, second, and third columns of the matrix 
$\mathbf{V}$ given by Eq. \ref{eq:V_triaxial_prolate},
in the case of a triaxial or prolate ellipsoid, or the
matrix $\mathbf{V}$ given by Eq. \ref{eq:V_oblate},
in the case of an oblate ellipsoid.

The magnetic modelling of an ellipsoidal body is commonly performed
in a particular Cartesian coordinate system that is aligned 
with the body semi-axes
and has the origin coincident with the body centre.
For convenience, we denominate this particular coordinate 
system as \textit{local coordinate system}.
The relationship between the Cartesian coordinates 
$(\tilde{x}, \tilde{y}, \tilde{z})$ of a point in 
a local coordinate system and the Cartesian 
coordinates $(x, y, z)$ of the same point in the main
system is given by:
\begin{equation}
\tilde{\mathbf{r}} = \mathbf{V}^{\top} \left( \mathbf{r} - \mathbf{r}_{c} \right) \: ,
\label{eq:coord_transformation}
\end{equation}
where 
$\tilde{\mathbf{r}} = [\begin{array}{ccc} \tilde{x} & 
                                          \tilde{y} & 
                                          \tilde{z} \end{array} ]^{\top}$,
$\mathbf{r}$ and $\mathbf{r}_{c}$
are defined in Eq. \ref{eq:ellipsoid_surface} and the matrix $\mathbf{V}$
is defined according to Eqs. \ref{eq:V_triaxial_prolate} or
\ref{eq:V_oblate}, depending on the ellipsoid type.
%Similarly, we may properly use the orthogonality of 
%matrix $\mathbf{V}$ to transform a generic 
%linear system $\mathbf{M} \mathbf{p} = \mathbf{d}$,
%referred to the main coordinate system, into a new
%linear system 
%$\tilde{\mathbf{M}} \, \tilde{\mathbf{p}} = \tilde{\mathbf{d}}$,
%referred to a local coordinate system, 
%as follows:
%\begin{equation}
%\underbrace{\mathbf{V}^{\top} \mathbf{M} \mathbf{V}}_{\tilde{\mathbf{M}}} \, 
%\underbrace{\mathbf{V}^{\top} \mathbf{p}}_{\tilde{\mathbf{p}}} = 
%\underbrace{\mathbf{V}^{\top} \mathbf{d}}_{\tilde{\mathbf{d}}} \: .
%\label{eq:matrix-transformation}
%\end{equation}

@@

Consider a magnetized ellipsoid immersed in
a uniform magnetic field $\mathbf{H}_{0}$ (in $\unit{Am^{-1}}$).
This uniform field can be, for example, the main component of the
Earth's magnetic field, which is usually assumed to be generated
by the Earth's liquid core.
In the absence of conduction currents, 
the total magnetic field $\mathbf{H}(\mathbf{r})$
at the position $\mathbf{r}$ (Eqs. \ref{eq:A} and 
\ref{eq:coord_transformation}) of a point referred to the main 
coordinate system is defined as follows \citep{sharma1966, 
eskola1980, reitz1992, sttraton2007}:
\begin{equation}
\mathbf{H}(\mathbf{r}) = \mathbf{H}_{0} - \nabla V(\mathbf{r}) \: ,
\label{eq:H}
\end{equation}
where the second term is the negative gradient of 
the magnetic scalar potential $V(\mathbf{r})$ given by:
\begin{equation}
V(\mathbf{r}) = -\frac{1}{4\pi} \iiint_{\vartheta} 
\mathbf{M}(\mathbf{r}^{\prime})^{\top} 
\nabla \left(
\frac{1}{\| \mathbf{r} - \mathbf{r}^{\prime} \|}
\right) \, dx^{\prime}dy^{\prime}dz^{\prime} \: .
\label{eq:phi-potential}
\end{equation}
In this equation, $\mathbf{r}^{\prime} = [\begin{array}{ccc} 
x^{\prime} & y^{\prime} & z^{\prime} \end{array} ]^{\top}$
is the position vector of a point located within the volume $\vartheta$, 
the integral is conducted over the variables 
$x^{\prime}$, $y^{\prime}$ and, $z^{\prime}$ representing
the coordinates of a point located within the volume $\vartheta$
of the ellipsoid, $\| \cdot \|$ denotes the Euclidean norm and 
$\mathbf{M}(\mathbf{r}^{\prime})$ is the magnetization vector
(in $\unit{Am^{-1}}$).
Eq. \ref{eq:phi-potential} is valid anywhere, 
independently if the position vector $\mathbf{r}$ represents
a point located inside or outside the magnetized body
\citep{dubois1896}.

@@

The scalar function $\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\dagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{0}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \in V \: ,
\label{eq:fi-tilde}
\end{equation}
where
\begin{equation}
R(u) = \sqrt{\left( a^{2} + u \right)\left( b^{2} + u \right)\left( c^{2} + u \right)} \: .
\label{eq:R}
\end{equation}
This function represents the gravitational potential
that would be produced by the ellipsoidal body at
points located within its volume $\vartheta$ if it
had a uniform density equal to the inverse of the
gravitational constant.
Notice that, in this case, the gravitational potential
is a quadratic function of the spatial coordinates
$\tilde{x}$, $\tilde{y}$, and $\tilde{z}$, which
supported the \citeauthor{maxwell1873}'s (\citeyear{maxwell1873})
postulate about uniformly magnetized ellipsoids.
In a similar way, the function $\tilde{f}^{\ddagger}(\tilde{\mathbf{r}})$
is given by
\begin{equation}
\tilde{f}^{\ddagger}(\tilde{\mathbf{r}}) = \pi \, abc \, 
\int_{\lambda}^{\infty} \left( 1 
- \frac{\tilde{x}^{2}}{a^{2} + u} 
- \frac{\tilde{y}^{2}}{b^{2} + u}
- \frac{\tilde{z}^{2}}{c^{2} + u} \right)
\frac{1}{R(u)} \, du \: , \quad \tilde{\mathbf{r}} \not\in V \: ,
\label{eq:fe-tilde}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and the
parameter $\lambda$ is defined according to the
ellipsoid type as a function of the spatial coordinates
 $\tilde{x}$, $\tilde{y}$, and $\tilde{z}$ (see Appendix B). 
For readers interested in additional information about the 
parameter $\lambda$, we recommend \citet[p.~234]{webster1904},
\citet[p.~184]{kellogg1929} and \citet{clark1986}.

The second important coordinate transformation is defined
with respect to Eq. \ref{eq:H-M-uniform}.
By properly using the orthogonality of matrix $\mathbf{V}$ 
(Eqs. \ref{eq:V_triaxial_prolate} and \ref{eq:V_oblate}),
the magnetic field $\mathbf{H}(\mathbf{r})$ 
(Eq. \ref{eq:H-M-uniform}) can be transformed
from the main coordinate system to a local coordinate system
as follows:
\begin{equation}
\underbrace{\mathbf{V}^{\top} \mathbf{H}(\mathbf{r})}_{\tilde{\mathbf{H}}(\tilde{\mathbf{r}})} = 
\underbrace{\mathbf{V}^{\top} \mathbf{H}_{0}}_{\tilde{\mathbf{H}}_{0}}
- \underbrace{\mathbf{V}^{\top} \mathbf{N}(\mathbf{r}) \mathbf{V}}
_{\tilde{\mathbf{N}}(\tilde{\mathbf{r}})} \;
\underbrace{\mathbf{V}^{\top} \mathbf{K} \mathbf{V}}
_{\tilde{\mathbf{K}}} \; 
\underbrace{\mathbf{V}^{\top} \mathbf{H}^{\dagger}}
_{\tilde{\mathbf{H}}^{\dagger}} \: ,
\label{eq:H-tilde}
\end{equation}
where the superscript "$\sim$" denotes quantities
referred to the respective local coordinate system.

In Eq. \ref{eq:H-tilde}, the transformed
depolarization tensor $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
is calculated as a function of the original depolarization
tensor $\mathbf{N}(\mathbf{r})$ (Eq. \ref{eq:H-M-uniform}).
In this case, the elements of $\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$
are calculated as a function of the second derivatives of the
function $f(\mathbf{r})$ (Eq. \ref{eq:f}),
which is defined in the main coordinate system.
It can be shown (Appendix A), however, that the
elements $\tilde{n}_{ij}(\tilde{\mathbf{r}})$ of
$\tilde{\mathbf{N}}(\tilde{\mathbf{r}})$ can also be calculated
as follows:
\begin{equation}
\tilde{n}_{ij}(\tilde{\mathbf{r}}) = - 
\frac{1}{4\pi} \frac{\partial^{2} \, \tilde{f}(\tilde{\mathbf{r}})}
{\partial \tilde{r}_{i} \, \partial \tilde{r}_{j}} 
\: , \quad i = 1, 2, 3 \: , \quad j = 1, 2, 3 \: ,
\label{eq:nij-tilde}
\end{equation}
where $\tilde{r}_{1} = \tilde{x}$, $\tilde{r}_{2} = \tilde{y}$, 
and $\tilde{r}_{3} = \tilde{z}$ are the elements of the
transformed vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
and $\tilde{f}(\tilde{\mathbf{r}})$ is given by Eq. \ref{eq:fi-tilde}
or \ref{eq:fe-tilde}, depending if $\tilde{\mathbf{r}}$ represents a
point located within or without the volume $\vartheta$ of the
ellipsoidal body.

@@

By considering $\tilde{\mathbf{r}}$ as a point within the
volume $\vartheta$ of the ellipsoid and using the Maxwell's postulate 
about the uniformity of the magnetic field $\mathbf{H}(\mathbf{r})$ 
inside ellipsoidal bodies, we can use Eq. \ref{eq:H-tilde}
for defining the resultant uniform magnetic field $\tilde{\mathbf{H}}^{\dagger}$
inside the ellipsoidal body as follows:
\begin{equation}
\tilde{\mathbf{H}}^{\dagger} = 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \: ,
\label{eq:Hi-tilde}
\end{equation}
where $\mathbf{I}$ is the identity matrix and 
$\tilde{\mathbf{N}}^{\dagger}$ represents the
transformed depolarization tensor evaluated within 
the volume $\vartheta$ of the ellipsoidal body. The elements
of $\tilde{\mathbf{N}}^{\dagger}$ will be presented in a 
latter section.

Let us pre-multiply the uniform internal field $\tilde{\mathbf{H}}^{\dagger}$
(Eq. \ref{eq:Hi-tilde}) by the transformed 
susceptibility tensor $\tilde{\mathbf{K}}$ 
(Eq. \ref{eq:H-tilde}) to obtain
\begin{equation}
\begin{split}
\tilde{\mathbf{M}} 
&= \tilde{\mathbf{K}} 
\left( \mathbf{I} - \tilde{\mathbf{N}}^{\dagger} \, \tilde{\mathbf{K}} \right)^{-1}
\tilde{\mathbf{H}}_{0} \\
&=  
\left( \mathbf{I} - \tilde{\mathbf{K}} \, \tilde{\mathbf{N}}^{\dagger} \right)^{-1}
\tilde{\mathbf{K}} \, \tilde{\mathbf{H}}_{0}
\end{split} \: ,
\label{eq:M-tilde}
\end{equation}
where $\tilde{\mathbf{M}}$
represents the transformed magnetization, as can be easily
verified by using Eqs. \ref{eq:M-KH} and \ref{eq:H-tilde}.
The matrix identity used for obtaining the second line of Eq. 
\ref{eq:M-tilde} is given by \citet[p. ~151]{searle1982}.
